---
title: "scatter_plot_logx"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{scatter_plot_logx}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(fancyplots)
library(dplyr)
library(gapminder)
```

`scatter_plot_logx`

HELLO! This vignette is essentially my README.md for the package. ENJOY!

## Examples with `scatter_plot_logx` 
#### making scatterplots with a logarithmically scaled x axis!!!
(the only function in this package :sweat_smile:)

##### Example 1: Numerical Y Axis
Here is how `fancyplots` *scatter_plot_x* function works with the gapminder dataset. In this example, our y axis will be *lifeExp*, which contains the average life expectancy of each country over the years.

This graph shows *population vs life expectancy* in the countries of Asia from 1952-2007.

```{r example1}
library(fancyplots)
library(gapminder)
example1 <- filter(gapminder, continent == "Asia")
scatter_plot_logx(example1, "pop", "lifeExp")
```

##### Example 2: Factors as the Y Axis
Here is how `fancyplots` *scatter_plot_x* function works with the gapminder dataset. In this example, our y axis will be *continent*. 

This graph shows us the spread of the population in the countries of each continent in 2007.

```{r example2}
library(fancyplots)
example2 <- filter(gapminder, year == 2007)
scatter_plot_logx(example2, "pop", "continent")
```

## Default Features

##### `na.omit`
The `scale_log_x` by default removes any NA's within your dataset via **na.omit** = TRUE!

Below is plotting of example 1 with multiple NAs inserted.
```{r example3}
#adding NAs to rows 150-250
example1[150:250, ] <- NA

scatter_plot_logx(example1, "pop", "lifeExp", na.omit = TRUE)
```

##### `logx`
The `scale_log_x` by default scales the x axis of your plot via **logx** = TRUE! 

Below is example 2, plotting with **logx** = FALSE

```{r example4}
scatter_plot_logx(example2, "pop", "continent", logx = FALSE)
```

##### `verbose`
Finally, the `scale_log_x` by default has a **verbose** option set to TRUE! This prints those update messages one sees prior to the plot. You can similarly turn off these messages by making **verbose** equal to FALSE. 
